Verifying Demonstrations

### 2020-03-13 paper/intro.tex

Our work present contributions in the area of \ac{DB} public-key protocols, 
particularly \ac{DB} \ac{ZKPK}.
This allows anyone to act as a verifier, unlike in the shared-key scenario 
where the verifier must be trusted.
The \ac{ZK} property also enables privacy properties such as anonymity.

@@

We make three contributions.
First, we provide a version of the Schnorr protocol that is \ac{DBMF}, 
\ac{DBTF}, \ac{DBDH} and \ac{DBDF} resistant in the \ac{DFKOmodel}.
This version is based on the assumption that we can transmit all bits at once, 
not bit-by-bit as normally required for \ac{DB}.
This assumption is reasonable by the results of \textcite{UWBPR}.

@@

The paper is organized as follows.
\Cref{Preliminaries} introduces the preliminaries of \ac{ZKPK} and \ac{DB}.
\Cref{DB-Schnorr} introduces the first version, where we assume that we can 
send all bits at the same time.
\Cref{DB-Schnorr-PKI} introduces the \ac{PKI} and \ac{AKE} to use the first 
version of the protocol in practice.
\Cref{DB-Schnorr-nbit} describes the bit-by-bit version of the protocol.
\Cref{formal-verification} describes our effort to formally verify the protocol 
using Tamarin.
Finally, we conclude with discussion and conclusions in 
\cref{Discussion,Conclusion}.

>>>>

Our work present contributions in the area of \ac{DB} public-key protocols, 
particularly \ac{DB} \acp{ZKPK}.
This allows anyone to act as a verifier, unlike in the shared-key scenario 
where the verifier must be trusted.
The \ac{ZK} property also enables a variety of privacy properties, such as 
anonymity.

@@

We make three contributions.
First, we provide a version of the Schnorr protocol that is \ac{DBMF}, 
\ac{DBTF}, \ac{DBDH} and \ac{DBDF} resistant in the \ac{DFKOmodel}.
This version is based on the assumption that we can transmit all bits at once, 
not bit-by-bit as normally required for \ac{DB}.
This assumption is motivated by the results of \textcite{UWBPR}.

@@

The paper is organized as follows.
\Cref{related-work} discusses related work.
\Cref{Preliminaries} introduces the preliminaries of \ac{ZKPK} and \ac{DB}.
\Cref{DB-Schnorr} introduces the first version, where we assume that we can 
send all bits at the same time.
\Cref{DB-Schnorr-PKI} introduces the \ac{PKI} and \ac{AKE} to use the first 
version of the protocol in practice.
\Cref{DB-Schnorr-nbit} describes the bit-by-bit version of the protocol.
\Cref{formal-verification} describes our effort to formally verify the protocol 
using Tamarin.
Finally, we conclude with discussion and conclusions in 
\cref{Discussion,Conclusion}.
